Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-10-08 paper.tex
more fixes

        \section{Platform-independence}
            Achieving platform-independence allows users to use the workflow 
            engine in any available environment. This however does not imply 
            that the tools, and as a consequence, the pipelines created will
            also be platform-independent. Many workflow engines have opted to 
            be platform independent. These workflow engines include: Nipype,
            PSOM, SPM, FASTR, LONI, AA, Pydpiper, Taverna, Toil, MapReduce, Spark and
            Dask. These workflow engines achieve platform independence through
            running on the Java Virtual Machine (JVM) being written in 
            Python or CWL. Platform-independent engines that run on the JVM include: 
            MATLAB engine frameworks, such as PSOM, SPM and AA; LONI; Taverna; 
            MapReduce; and Spark \tristan{this list contains Matlab
            engines}. Nipype, FastR, Pydpiper are all python-based platform 
            independent workflow engines and Toil is CWL-based platform independent. 
            The remainder of the 
            workflow engines (Pegasus, Make, OpenMOLE, Nextflow and Galaxy are 
            not platform-independent, but can execute on macOS and Linux.

>>>>

        \section{Platform-independence}
            Achieving platform-independence allows users to use the workflow 
            engine in any available environment. This however does not imply 
            that the tools, and as a consequence, the pipelines created will
            also be platform-independent. Many workflow engines have opted to 
            be platform independent. These workflow engines include: Nipype,
            PSOM, SPM, FASTR, LONI, AA, Pydpiper, Taverna, Toil, MapReduce, Spark and
            Dask. These workflow engines achieve platform independence through
            running on the Java Virtual Machine (JVM) being written in 
            Python or CWL. Platform-independent engines that run on the JVM include: 
            MATLAB engine frameworks, such as PSOM, SPM and AA; LONI; Taverna; 
            MapReduce; and Spark \tristan{this list contains Matlab
            engines}. Nipype, FastR, Pydpiper are all python-based platform 
            independent workflow engines and Toil and Galaxy are CWL-based 
            platform independent engines. 
            The remainder of the 
            workflow engines (Pegasus, Make, OpenMOLE and Nextflow are 
            not platform-independent, but can execute on macOS and Linux.
